Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
edits

\textbf{\textit{Web server.}} As one of our primary goals of adding effect
handlers to OCaml is to support direct-style concurrency, we implement a
full-fledged HTTP/1.1 web server using effect handlers (|MC|). We use effect
handlers to implement a user-level threading library, which spawns a thread per
request. We use \texttt{httpaf} library~\cite{httpaf} for HTTP handling, and
\texttt{libev}~\cite{libev} for the eventloop. We compare our implementation
against an Lwt version (|lwt|) which also uses \texttt{httpaf} and
\texttt{libev}. Unlike using effect handlers, Lwt version is written in monadic
style, and does not have a notion of thread per request. For comparison, we
also include a Go 1.13 version (|go|) that uses
\texttt{net/http}~\cite{nethttp} package. As both the OCaml versions are single
threaded, the Go benchmark is run with \texttt{GOMAXPROCS=1}.

>>>>

\textbf{\textit{Web server.}} As one of our primary goals of adding effect
handlers to OCaml is to support direct-style concurrency, we implement a
full-fledged HTTP/1.1 web server using effect handlers (|MC|). We use effect
handlers to implement a user-level threading library that spawns a thread per
request. We use \texttt{httpaf}~\cite{httpaf} for HTTP handling, and
\texttt{libev}~\cite{libev} for the eventloop. We compare our implementation
against an Lwt version (|lwt|) which also uses \texttt{httpaf} and
\texttt{libev}. Unlike using effect handlers, the Lwt version is written in monadic
style and does not have a notion of thread per request. For comparison, we
also include a Go 1.13 version (|go|) that uses the
\texttt{net/http}~\cite{nethttp} package. As both the OCaml versions are single
threaded, the Go benchmark is run with \texttt{GOMAXPROCS=1}.
